Efficient Coalition Formation \\ for Web Services

### 2013-05-26 papers/coalition-journal-extension/coalition_journal.tex
Changes

Figure \ref{fig_community} represents the architecture of web service communities. The communities are basicly as an abstraction model of web services, they aggrigate web services and communicate with UDDI registeries and users using same protocols as web services. Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Communitiy coordinators try to attract quality web services and keep the community as stable as possible. The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

>>>>

Figure \ref{fig_community} represents the architecture of web service communities. The communities are basicly an abstract model of web services, they aggrigate web services and communicate with other entities such as UDDI registeries and users, using identical protocols as web services. Web services join communities to increase their utility by having a larger market share and task pool. Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Communitiy coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
